\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-03-01 paper.tex
Rachid comments

A third example relates to human-robot interaction scenarios where \emph{perspective
taking} is important (a prototypical example being the game `I spy with my
little eye', as implemented in~\cite{ros2010which}). Perspective taking is a
cognitive skill that relies on the ability for an agent to take someone else's
point of view to estimate what they see from their perspectives. 
Perspective taking has previously been implemented in robotics by temporarily placing
virtual cameras at eye locations for each of the humans tracked by the
robot~\cite{ros2010solving}. While acceptable for simple cases, such an approach
does not maintain truly independent models of the environment for each
agent, and in particular does not permit false-belief
modelling~\cite{lemaignan2015mutual} whereas separate, independent world models
would effectively support such a skill.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{laasudws}
    \caption{Schema of the \uwds architecture used in the MuMMER project.
    Clients (blue boxes) read and generate worlds (whose names are in typewriter
    fonts).}
    \label{fig|mummerarchitecture}
\end{figure}
%The interaction scenario requires a number of \uwds clients. The clients are
%distributed across...

>>>>

A third example relates to human-robot interaction scenarios where
\emph{perspective taking} is important (a prototypical example being the game `I
spy with my little eye', as implemented in~\cite{ros2010which}). Perspective
taking is a cognitive skill that relies on the ability for an agent to take
someone else's point of view to estimate what they see from their perspectives.
Perspective taking has previously been implemented in robotics by temporarily
placing virtual cameras at eye locations for each of the humans tracked by the
robot~\cite{ros2010solving}. While acceptable for simple cases, such an approach
does not maintain truly independent spatio-temporal models of the environment
for each agent, and in particular, it does not permit the representation of
proper false-belief situations. On the contrary, separate, independent world
models as implemented by \uwds effectively support such a skill, which is an
important precursor to research and implement human's mind modelling (\ie a
theory of mind)~\cite{lemaignan2015mutual}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{laasudws}
    \caption{Schema of the \uwds architecture used in the MuMMER project.
    Clients (blue boxes) read and generate the worlds whose names are in typewriter
    fonts. The last two worlds, {\tt HUMAN\{1,2\}\_PERSPECTIVE}, do not only
    represent the immediate visual perspective of the two humans, but integrate
    as well their past visual perceptions. As such, they are the \emph{visual
    memories} of the humans, that the robot can rely on when making decisions.}
    \label{fig|mummerarchitecture}
\end{figure}
%The interaction scenario requires a number of \uwds clients. The clients are
%distributed across...
